---
title: "R Notebook"
output: html_notebook
---
 

```{r}

# +++++++++++++++++ #
#                   # 
#    LIBRARIES
#                   #
# +++++++++++++++++ #

# Installation of required packages
install.packages("dagitty")
install.packages("ggdag")
install.packages("causaleffects")


```


```{r}


# Load packages

library(dagitty)
library(ggdag)

library(causaleffect)

library(readr) #to read csv 
library(tidyverse) #for everything 
library(dplyr) #for everything 

# +++++++++++++++++ #
#                   # 
#READ IN SCRAPED DATA
#                   #
# +++++++++++++++++ #

files.lit <- 
    list.files(path = "RawFiles_do_not_upload/", # read all excel fileNAMES from this folder
                       pattern = "*.csv",
                       full.names = TRUE,
                       recursive = FALSE) %>% 
    tbl_df() %>% # make the list into a dataframe, default name of column is "value"
    rename(Filenames = value)%>%
    mutate(myFiles = purrr::map(Filenames, function(x) {  #for each filename, read in the file (gets nested)
        read_csv(x)})) %>% 
    unnest(myFiles)  

# +++++++++++++++++ #
#                   # 
#ORGANIZE DATA BY KEY
#                   #
# +++++++++++++++++ # 

dat.lit <-
    files.lit %>%
    select(Filenames,Title,Year,Cites,Authors) %>%  # parse to only the relevant columns
    filter(Cites>1) %>% # get rid of a uncited papers
    mutate(Category = case_when(  #simplify the categories
            Filenames=="RawFiles_do_not_upload/Energy_Buildings_PoPCites.csv" ~ "Energy",
            Filenames == "RawFiles_do_not_upload/Health_Buildings_PoPCites.csv" ~ "Health",
            Filenames == "RawFiles_do_not_upload/IEQ_searchPoPMetrics.csv" ~ "IEQ",
            TRUE ~ "Other")) %>%
    mutate(Category = as.factor(Category)) %>% # needs to be a factor for grouping later on
    select(-Filenames) %>% # we created Categories for this instead 
    drop_na(Year) # Get rid of papers without a publication date (3 in Health and 3 in IEQ)
    
dat.lit %>% # just a quick check to see spread of years of publication, by category
    group_by(Category) %>%
    summarize(count=n(),ealiest=min(Year))

dat.lit2 <- # make new categories for overlaps 
    dat.lit %>%
    group_by(Title,Year,Cites,Authors) %>%
    summarize(Recategorized = paste(Category,collapse = '_'))  # # also needs to be a factor for grouping later on...


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
